\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png}\\ \vspace{5mm} LFEUI - Investigation Proposal \\ \vspace{0mm} {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-0mm}

### 2023-12-02 text/proposta/prop.tex
final

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[letterpaper,top=10mm,bottom=15mm,left=10mm,right=10mm,marginparwidth=1.75cm]{geometry}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{makecell}
\usepackage{titlesec}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{makecell}
\usepackage{url}
\usepackage{csquotes}
\usepackage{caption}
\usepackage{enumitem}
\usepackage{textcomp}
\usepackage{pdflscape}
\usepackage{makeidx}
% \usepackage{tocbibind}
\providecommand{\tightlist}{\relax}
\usepackage{tocloft}
\renewcommand{\cftsecindent}{0em}
\renewcommand{\cftsubsecindent}{1em}
\renewcommand{\cftsecfont}{\bfseries}
\renewcommand{\cftsubsecfont}{\itshape}
\setlength{\cftsubsecnumwidth}{0em}

@@

\title{\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png}\\ \vspace{5mm}
LFEUI - Investigation Proposal \\ \vspace{4mm} {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-1mm}}
\date{November 2023}

@@

\begin{center}
  \textbf{\Large Abstract}
\end{center}

% \begin{abstract}
%   \par textvtgerthrt
% \end{abstract}

\par In the following document we present a proposal for a scientific research being developed at CTN Lisbon. We will...

\vspace{4.0mm}

@@

We will obtain the energy spectrum of the alpha particles resulting from the reaction between the protons and the
samples. 
For the glass samples, we expect to see a profile due to the particles that come from different depths of the sample and
therefore have lost different amounts of energy. In the implant samples, we expect to see a peak at the energy corresponding
to the energy of the alpha particles produced by the reaction.
In both cases, the samples are composed by other types of atoms such as silicon and boron, which will also emit charged
particles. By obtaining the expected energy spectrums we can infer the presence of Li in the samples. If possible we will also try
to quantify the amount of Li present by analysing the amout of energy deposited in the spectrums.

>>>>

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[letterpaper,top=6mm,bottom=15mm,left=6mm,right=6mm,marginparwidth=1.55cm]{geometry}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{makecell}
\usepackage{titlesec}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{makecell}
\usepackage{url}
\usepackage{csquotes}
\usepackage{caption}
\usepackage{enumitem}
\usepackage{textcomp}
\usepackage{pdflscape}
\usepackage{makeidx}
% \usepackage{tocbibind}
\providecommand{\tightlist}{\relax}
\usepackage{tocloft}
\renewcommand{\cftsecindent}{0em}
\renewcommand{\cftsubsecindent}{1em}
\renewcommand{\cftsecfont}{\bfseries}
\renewcommand{\cftsubsecfont}{\itshape}
\setlength{\cftsubsecnumwidth}{0em}

@@

\title{\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png}\\ \vspace{5mm}
LFEUI - Investigation Proposal \\ \vspace{0mm} {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-0mm}}
\date{November 2023}

@@

% \begin{center}
%   \textbf{\Large Abstract}
% \end{center}

\vspace{-0.1cm}
\begin{abstract}
  \par In the following document we present a proposal for a scientific research being developed at CTN Lisbon in December 2023.
  Our work consists of the detection of $\ce{^7Li}$ in two different samples through nuclear reactions.
  This document describes the time required for the project as well as it's goals, theoretical background, experimental technique, safety considerations and expected results.
  In addition, we also present a brief description of the experimental set-up.
\end{abstract}
\vspace{-0.1cm}

@@

We will obtain the energy spectrum of the alpha particles resulting from the reaction between the protons and the
samples. 
For the glass samples, we expect to see a profile due to the particles that come from different depths of the sample and
therefore have lost different amounts of energy. In the implant samples, we expect to see a peak at the energy corresponding
to the energy of the alpha particles produced by the reaction.
In both cases, the samples are composed by other types of atoms such as silicon and boron, which will also emit charged
particles. By obtaining the expected energy spectrums we can infer the presence of Li in the samples. If possible we will also try
to quantify the amount of Li present by analyzing the amount of energy deposited in the spectrums.
